%-----------------------------------------------------------Header Starts--------------------------------------

\documentclass[main.tex]{subfiles}

%-----------------------------------------------------------Header Ends--------------------------------------


\thispagestyle{fancy}
\fancyhf{}
%\rhead{Page \thepage}
%\lhead{\chaptername \ \thechapter}
\cfoot{Page \thepage}


\begin{document}


\chapter*{\vspace{-2cm}Acknowledgements}

\noindent In the Name of Allah, the Most Gracious and the Most Merciful\\

\noindent Alhamdulillah, all praises to Almighty Allah for the strengths and His blessing in completing this thesis.
I would like to thank my supervisor \textbf{Dr. Md. Fakhrul Islam} for giving me the opportunity to work in the department of Glass and Ceramic Engineering at BUET. There are not enough words for expressing my sincere gratitude for his willingness to share his knowledge with me through numerous discussions and support since the time of my coursework to completion this degree.\\

\noindent I am immensely grateful to \textbf{Dr. A. K. M. Abdul Hakim} for his interest in my work, and encouragement and insight through these years. It was his guidance and support that helped me through all the difficult time. I will surely benefit from his creative thoughts, suggestions and dedication throughout the rest of my life. The same gratitude goes to \textbf{Dr. M. A. Matin} for his kind help and support on my research and my life during the past two years.\\

\noindent I also want to thank \textbf{Dr. Md. Abdullah Zubair} for thoughtful discussions and sharing his knowledge which inspired me to become a perfectionist researcher in coming years. I would like to express a special word of thanks to my teachers \textbf{Dr. Muhammad Hasanuzzaman, Arman Hussain $\&$ Mehedi Hasan Rizvi} for their continuous support and inspiration during my M.Sc. study.\\

\noindent My warmest thanks go to \textbf{Dr. S. A. M. Tofail} from University of Limerick, Ireland for giving his valuable time and thoughts for my thesis work including the state of the art laboratory facilities to characterize my samples. I would like to express my gratitude to \textbf{Dr. Vasily Lebedev} and \textbf{Dr. Karrina McNamara} at University of Limerick, Ireland for carrying out the TEM and XPS measurements of my samples. I also want to thank \textbf{Dr. Sheikh Manjura Hoque}, Chief Scientific Officer and Head, Materials Science Division, Atomic Energy Centre, Bangladesh Atomic Energy Commission, for her support with the magnetic characterization facilities.\\

\noindent I would like to convey my heartiest regards to all of the faculty members, technical and official staff of Department of Glass and Ceramic Engineering at BUET for their assistance and cooperation during this whole time.\\

\noindent Finally, I want to thank my beloved parents and my wife \textbf{Manifa Noor} for being there for me. Without their love, understanding and encouragement, this work would be close to impossible to finish.\\


\thispagestyle{fancy}
\newpage

\end{document}







